Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/evaluation.tex
Backup
exp 4.4

\subsection{Arm Pose Estimation}
\label{exp:benchmark}
Two experiments are undertaken in this section: 1) presenting training classic patch AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch AAM from joint annotation .

@@

\subsection{Non-rigid Object Alignment In-the-wild}
\label{exp:daam_benchmark}
\begin{figure}[b!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/face}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/ear}
    \end{subfigure}
    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:daam_benchmark}}
    \label{fig:daam_benchmark}
\end{figure}

@@

>>>>

\subsection{Arm Pose Estimation}
\label{exp:benchmark}

Two experiments are undertaken in this section: 1) presenting training classic patch AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch AAM from joint annotation .

@@

\subsection{Non-rigid Object Alignment In-the-wild}
\label{exp:daam_benchmark}

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.25\columnwidth]{resources/DAAMBenchmark/legend}
    \\
    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/face}
    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/ear}
    \caption{CEDs of faces and ears fitting performance for experiment \ref{exp:daam_benchmark}}
    \label{fig:daam_benchmark}
\end{figure}

@@

\begin{figure*}[t!]
    \centering
    \includegraphics[height=\fh]{resources/Fixing/fix_3}
    \includegraphics[height=\fh]{resources/Fixing/fix_5}
    \includegraphics[height=\fh]{resources/Fixing/fix_6}
    \includegraphics[height=\fh]{resources/Fixing/fix_7}
    \includegraphics[height=\fh]{resources/Fixing/fix_8}
    \includegraphics[height=\fh]{resources/Fixing/fix_9}
    \includegraphics[height=\fh]{resources/Fixing/fix_10}
    \includegraphics[height=\fh]{resources/Fixing/fix_12}
    \includegraphics[height=\fh]{resources/Fixing/fix_13}
    \includegraphics[height=\fh]{resources/Fixing/fix_14}
    \includegraphics[height=\fh]{resources/Fixing/fix_15}
    \includegraphics[height=\fh]{resources/Fixing/fix_17}
    \includegraphics[height=\fh]{resources/Fixing/fix_18}
    \includegraphics[height=\fh]{resources/Fixing/fix_19}
    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}}
    \label{fig:qualitative}
\end{figure*}
